SDC: Social Dispersed Computing

### 2017-06-23 papers/IARPA-RFI-17-03/rfi.tex
new section

>>>>

\subsection{Blockchains for SDC: Opportunities and Challenges}

One of the key challenges in social dispersed computing is ensuring that NCPs that are operated by multiple parties, who may have limited trust in each other, can work together.
For example, in transactive energy, devices belonging to individual prosumers, industrial consumers/producers, and DSOs have to coordinate and share information with each other.
Since these parties have different goals, privacy concerns, and security practices, it is hard to establish a common application platform.
Moreover, the transactive systems also has to satisfy the stringent security and safety requirements of power grids, which imposes further constraints on coordination.  
Likewise, in multimodal routing, computational components belonging to the government, private companies, and individual users have to work together, despite having limited trust in each other.

Blockchain based computational platforms may act as a key enabling technology for social dispersed computing, by solving the above coordination problem.
Using blockchain technology, the NCPs can reach consensus on any state variable in the system, without relying on a trusted third party or trusting each other.
For example, NCPs within a transactive energy system can reach consensus on energy prices, which is crucial for the stability of the grid.
Further, distributed consensus not only solves the trust issue, but also provides fault-tolerance since consensus is always reached on the correct state as long as the number of faulty NCPs is below a threshold.

In a blockchain based platform, transitions between system states are recorded as transactions in a ledger.
To reach system-wide consensus, NCPs must share transactions with all other participants in a system.
Ironically, the public nature of the ledger is a double-edged sword, which poses severe threats to privacy.
As every state change must be published as a transaction, it is impossible to keep certain state variables confidential.
This is clearly unacceptable for most social dispersed computing applications, which handle sensitive personal information, such as individual users' locations or real-time energy usage data of individual households.

The current solution to this privacy problem is to publish certain state variables in an encrypted form (e.g., encrypted energy usage data), which can be decrypted only by authorized entities.
However, this solution has fundamental limitations.
Since NCPs must reach consensus on the state of the system, any state update that is based on the values of encrypted variables requires that a majority of NCPs be able to decrypt the variables, which would clearly violate the privacy of the encrypted variables.
As a consequence, privacy-preserving systems cannot perform computations based on private values.

To enable the next step in the evolution of decentralized computing, blockchain platforms must be extended with functionality that allows them to perform computations on encrypted variables.
In this direction, homomorphic encryption can act as an enabling technology.
Using homomorphic encryption, NCPs can perform computation on private state variables without learning their values.
For example, in a transactive energy system, individual households' real-time energy consumption may be encrypted with a homomorphic encryption scheme and published on the distributed ledger.
Then, every NCP in the system is able to compute the encrypted aggregate energy consumption by adding together the encrypted individual consumption values.
This allows the NCPs to reach consensus on state variables without learning their values.
